\bf Title here

### 2020-08-20 paper/paper.Rmd
more changes in plot definition section

Sometimes, rather than exploring the searching points, we may be interested in exploring the points on the interpolation path (target and interpolating points) since these points will be played by the tour animation. Since interpolation paths are geodesically the shortest, a summarisation using boxplot geometry is no longer needed. The slightly modified plot definition is shown below:

@@

*Toy example* A toy example is shown in Figure \ref{toy-interp}.

@@

In projection pursuit, the projection bases $\mathbf{A}_{p \times d}$ are usually of dimension $p \times d$ and hence can't be visualised in a 2D plot. An option to explore the searching space of these bases is to explore a reduced space via principal component analysis (PCA). The visualisation can thus be defined as

@@

<!-- In this way, the first two principle components will take up the x and y axis and all the other information will be mapped using other aesthetic attribution. [need to think further about how different type of variables can be shown].  -->

*A toy example: understand different stage of search_geodesic* `search_geodesic` is a two-stage ascending algorithm with four different stages in the search and a PCA plot useful to understand how the algorithm progresses and the relative position of each basis in the PCA projected 2D space. Starting from the start basis, a directional search is conducted in a narrow neighbourhood on five random directions. The best one is picked and a line search is then run on the geodesic direction to find the target basis. The starting and target bases are then interpolated. In the next iteration, the target basis becomes the current basis and then the procedures continues. A toy example is shown in Figure \ref{toy-pca}.

>>>>

Sometimes, we may be interested in exploring the points on the interpolation path since these are the points that will be played by the tour animation. The plot definition is as follows:

@@

Figure \ref{toy-interp} shows the plot of interpolating points and it shows the algorithm starts from around 0.8 and with interpolation, gradually reaches over 0.95.

@@

In projection pursuit, the projection bases $\mathbf{A}_{p \times d}$ are of dimension $p \times d$ with $p$ usually greater than two and hence can't be visualised in a 2D plot. An option to explore the searching space of these bases is to explore a reduced space via principal component analysis (PCA). The visualisation can thus be defined as

@@

Figure 5 shows the searching space plot of a geodesic search, colored by different searching stages. Starting from the start basis, a directional search is conducted in a narrow neighbourhood on five random directions. The best one is picked and an exact search finds the stepsize that maximises the index value and output the corresponding projection basis.

### 2020-08-20 paper/paper.tex
more changes in plot definition section

\emph{Toy example} A toy example is shown in Figure \ref{toy-interp}.

@@

In projection pursuit, the projection bases \(\mathbf{A}_{p \times d}\)
are usually of dimension \(p \times d\) and hence can't be visualised in
a 2D plot. An option to explore the searching space of these bases is to
explore a reduced space via principal component analysis (PCA). The
visualisation can thus be defined as

@@

\emph{A toy example: understand different stage of search\_geodesic}
\texttt{search\_geodesic} is a two-stage ascending algorithm with four
different stages in the search and a PCA plot useful to understand how
the algorithm progresses and the relative position of each basis in the
PCA projected 2D space. Starting from the start basis, a directional
search is conducted in a narrow neighbourhood on five random directions.
The best one is picked and a line search is then run on the geodesic
direction to find the target basis. The starting and target bases are
then interpolated. In the next iteration, the target basis becomes the
current basis and then the procedures continues. A toy example is shown
in Figure \ref{toy-pca}.

>>>>

Figure \ref{toy-interp} shows the plot of interpolating points and it
shows the algorithm starts from around 0.8 and with interpolation,
gradually reaches over 0.95.

@@

In projection pursuit, the projection bases \(\mathbf{A}_{p \times d}\)
are of dimension \(p \times d\) with \(p\) usually greater than two and
hence can't be visualised in a 2D plot. An option to explore the
searching space of these bases is to explore a reduced space via
principal component analysis (PCA). The visualisation can thus be
defined as

@@

Figure 5 shows the searching space plot of a geodesic search, colored by
different searching stages. Starting from the start basis, a directional
search is conducted in a narrow neighbourhood on five random directions.
The best one is picked and an exact search finds the stepsize that
maximises the index value and output the corresponding projection basis.
